---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# RUnitTesting

These are my notes on unit testing in R developed for the [Sheffield R User Group](http://sheffieldr.github.io/) on 6 March 2018.


## Setup

We need to install a few packages to perform tests and check test coverage.
`usethis` makes the setup easier.

```{r install-usethis, eval=FALSE}
install.packages(c("usethis", "testthat", "covr"))
```

`usethis` expects your project to behave like a package, so we should add a `DESCRIPTION`:

```{r use-description, eval=FALSE}
usethis::use_description()
```

It also wouldn't hurt to [add a license](http://r-pkgs.had.co.nz/description.html#license) and a [README](http://r-pkgs.had.co.nz/release.html#important-files).

Then set up our testing framework:

```{r use-testthat, eval=FALSE}
usethis::use_testthat()
```


## Remote automated testing (advanced)

We won't be automating these checks with continuous integration or test coverage services because:

1. These tend to be most useful for package developers
1. They're quite involved to set up correctly
1. It typically requires uploading a copy of any data sets for testing, which is not practical if the data are protected and/or larger than a few MB.

If you do want to set this up you need to:

1. Set up `travis` (`usethis::use_travis()`)
1. Set up coverage (`usethis::use_coverage()`). Both `coveralls.io` and `codecov.io` are free for open source projects, and `codecov.io` allows you to test coverage for one private github repo.
